Paper Figures and Text

### 2024-03-12 Fish Data Analysis/NN_Accel_Heading.qmd
Adding Heading PS to the paper script

## Loading in the Libraries for Everything
```{r}
library(MASS)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(viridis)
```

@@

fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))

@@

min_dist <- 0
max_dist <- 0.75

fish_data_nn <- fish_comp_data %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(#nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = nth_min(Distance, 1),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    #filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    #filter(row_n == 1) %>%
                                    ungroup() %>%
                                    mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS) %>%
                                    filter(Distance >= min_dist & Distance <= max_dist)

@@

manual_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
                   data = fish_data_nn_model) 
Anova(manual_model)

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line()+
  geom_line(aes(y = rad2deg(predict(manual_model,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  ylim(-50,50) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("All Fish From ",min_dist," to ",max_dist))

@@

>>>>

## Loading in the Libraries for Everything

```{r}
library(MASS)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(viridis)
library(lme4)
```

@@

fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))

@@

# fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
#                                               Fish3_X = Fish1_X,
#                                               Fish3_Y = Fish1_Y,
#                                               Fish3_Z = Fish1_Z,
#                                               Fish3_Speed = Fish1_Speed,
#                                               Fish3_Accel = Fish1_Accel,
#                                               Fish3_Yaw_Heading = Fish1_Yaw_Heading,
#                                               Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
#                                               ) %>%
#                                        mutate(Fish1 = Fish2,
#                                               Fish1_X = Fish2_X,
#                                               Fish1_Y = Fish2_Y,
#                                               Fish1_Z = Fish2_Z,
#                                               Fish1_Speed = Fish2_Speed,
#                                               Fish1_Accel = Fish2_Accel,
#                                               Fish1_Yaw_Heading = Fish2_Yaw_Heading,
#                                               Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
#                                        mutate(Fish2 = Fish3,
#                                               Fish2_X = Fish3_X,
#                                               Fish2_Y = Fish3_Y,
#                                               Fish2_Z = Fish3_Z,
#                                               Fish2_Speed = Fish3_Speed,
#                                               Fish2_Accel = Fish3_Accel,
#                                               Fish2_Yaw_Heading = Fish3_Yaw_Heading,
#                                               Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
#                                        #Switch around angle when we switch focal fish
#                                        mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi),
#                                               Relative_X = -1*Relative_X) %>%
#                                        select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))
# 
# fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)

min_dist <- 0
max_dist <- 3

fish_data_nn <- fish_comp_data %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(#nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = nth_min(Distance, 1),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    #filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    #filter(row_n == 1) %>%
                                    ungroup() %>%
                                    filter(Distance >= min_dist & Distance <= max_dist)

@@

@@

manual_model <- lm(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
                   data = fish_data_nn_model) 
Anova(manual_model)

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line()+
  geom_line(aes(y = rad2deg(predict(manual_model,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  ylim(-50,50) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("Nearest Neighbor From ",min_dist," to ",max_dist))

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Re graphing with new data
Adding Heading PS to the paper script

## Fish Turning Graphs

@@

abalated_dark_turning_data <- read.csv("Data/ablated_dark_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           select(-c("Singles","Frame","Fish")) %>%
                           mutate(Type = "Eight Fish")

annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
                           #filter(Next.to.Wall == 0) %>%
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>% 
                           select(-c("Turn.Start.Frame","Turn.End.Frame","Fish","Appox.Turn.Angle","X","Next.to.Wall")) %>%
                           rename("Turn_Dir" = "Turn.Direction")  %>%
                           rename("Fish_Left" = "No..Fish.Left")  %>%
                           rename("Fish_Right" = "No..Fish.Right")  %>%
                           mutate(Type = "Eight Fish")

single_fish_turning_data <- read.csv("Data/single_fish_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           select(-c("Singles")) %>%
                           mutate(Type = "Combined Single")

eight_fish_turning_data <- rbind(annushka_turning_data,abalated_dark_turning_data)

all_turning_data <- rbind(eight_fish_turning_data,single_fish_turning_data)

eight_fish_data_sum  <- eight_fish_turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()

single_fish_data_sum  <- single_fish_turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup() %>%
                                     filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation")

turning_data_sum <- all_turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()
```

### All the Plots of Eight Fish in Flow and Still, Raw and GLM

```{r}
eight_fish_still <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Still Water"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

eight_fish_flow <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

eight_fish_still
eight_fish_flow

### All the Plots of Eight Fish vs Single in Still Water

```{r}
placeholder_tibble <- tibble("Fish_Ratio" = c("0:7"),
                             "Fish_Num_Ratio" = c(0.875),
                             "Flow" = c("Still Water"),
                             "Ablation" = c("No Ablation"),
                             "Darkness" = c("Light"),
                             "Type" = c("Combined Single"),
                             "n" = c(0))

light_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

light_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "Ablated") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

dark_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "No Ablation") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

dark_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "Ablated") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

light_eight_and_single_graph <- ggplot(light_no_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

ablation_eight_and_single_graph <- ggplot(light_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

dark_eight_and_single_graph <- ggplot(dark_no_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

dark_ablation_eight_and_single_graph <- ggplot(dark_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph
dark_ablation_eight_and_single_graph
```

### Now we combine it all

```{r}
# turning_mega_plot <- ggarrange(eight_fish_still, eight_fish_flow,ggplot() + theme_classic() + theme(axis.line=element_blank()),
#           light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
#           labels = c("A", "B", "", "C", "D", "E"),
#           ncol = 3, nrow = 2)
# 
# ggsave("Paper Figures/turning_mega_plot.png", turning_mega_plot, width = 20, height = 12)

turning_both_plot <- ggarrange(eight_fish_still, eight_fish_flow,
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

ggsave("Paper Figures/turning_both_plot.png", turning_both_plot, width = 12, height = 6)

turning_single_test_plot <- ggarrange(
          light_eight_and_single_graph, ablation_eight_and_single_graph, 
          dark_eight_and_single_graph, dark_ablation_eight_and_single_graph,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 10, height = 7)

@@

>>>>

Heading Velocity graphs

```{r}
fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))

fish_comp_data <- na.omit(fish_comp_data)

min_dist <- 0
max_dist <- 2

fish_data_nn_normal <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
                                        group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                        ungroup()

nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()
```

Model and Graph

@@

heading_PS_model_still <- lm(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
                   data = fish_data_nn_normal %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_still)

heading_PS_graph <- ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_still,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  ylim(-50,50) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

heading_PS_graph

ggsave("Paper Figures/Heading_PS_Graph.jpg", heading_PS_graph, width = 7, height = 7)

@@

school_stats_mega_plot

school_stats_mega_plot <- annotate_figure(school_stats_mega_plot, 
                top = text_grob("                 Still Water                                     Flowing Water (2 BL/s)",
                                size = 24),
                fig.lab.pos = "top")
